Follow-up Samples

### 2017-02-20 submission/manuscript_outline_20161024.Rmd
background corrections

Recently, there has been promising work on the bacterial microbiome and it's ability to complement existing screening methods such as Fecal Immunoglobulin Test (FIT) or act alone as a screening tool [@baxter_microbiota-based_2016; @zeller_potential_2014]. There has also been research into how the bacterial microbiome could be altered directly on tumor tissue itself [@dejea_microbiota_2014].  A few studies have also shown how this microbiome [@zackular_manipulation_2016] or specific members within it [@arthur_microbial_2014] could be directly involved with the pathogenesis of CRC.  These studies have helped to provide a tantalizing link between the bacterial microbiome and CRC. Although these studies suggest that the bacterial microbiome might change after treatment there remains limited information on the bacterial microbiome before and after surgical removal of lesion (adenoma or carcinoma) and whether the community changes at all.

In this study we tested the hypothesis that the bacterial microbiome changes between pre (initial) and post (follow up) samples after removal of a lesion (adenoma or carcinoma).  Our analysis included both alpha and beta diversity analysis along with investigation of individual operational taxonomic units (OTUs).  We also utilized Random Forest to build models to classify either initial and follow up samples or lesion and normal samples and then subsequently observe how these models, as well as specific OTUs within them, performed pre and post surgery.  We also investigated the models for similar important OTUs to identify the crucial OTUs for not only classifying initial and follow up samples but also lesion or normal.

>>>>

Recently, there has been promising work on the bacterial microbiome and it's ability to complement existing screening methods such as Fecal Immunoglobulin Test (FIT) or act alone as a screening tool [@baxter_microbiota-based_2016; @zeller_potential_2014]. There has also been research into how the bacterial microbiome could be altered directly on tumor tissue itself [@dejea_microbiota_2014].  A few studies have also shown how this bacterial microbiome [@zackular_manipulation_2016] or specific members within it [@arthur_microbial_2014] could be directly involved with the pathogenesis of CRC.  These studies have helped to provide a tantalizing link between the bacterial microbiome and CRC. Although these studies suggest that the bacterial microbiome might change after treatment there remains limited information on the bacterial microbiome before and after surgical removal of lesion (adenoma or carcinoma) and whether the community changes at all.

In this study we tested the hypothesis that the bacterial microbiome changes between pre (initial) and post (follow up) samples removal of lesion (adenoma or carcinoma).  Our analysis included both alpha and beta diversity analysis along with investigation of individual operational taxonomic units (OTUs).  We also utilized Random Forest to build models to classify either lesion and normal samples or initial and follow up samples and then subsequently observe how these models, as well as specific OTUs within them, performed pre and post lesion removal.  We also investigated the models for similar important OTUs to identify the crucial OTUs for not only classifying lesion or normalsamples but also initial and follow up.

### 2017-02-20 submission/manuscript_outline_20161024.tex
background corrections

Recently, there has been promising work on the bacterial microbiome and
it's ability to complement existing screening methods such as Fecal
Immunoglobulin Test (FIT) or act alone as a screening tool {[}3,4{]}.
There has also been research into how the bacterial microbiome could be
altered directly on tumor tissue itself {[}5{]}. A few studies have also
shown how this microbiome {[}6{]} or specific members within it {[}7{]}
could be directly involved with the pathogenesis of CRC. These studies
have helped to provide a tantalizing link between the bacterial
microbiome and CRC. Although these studies suggest that the bacterial
microbiome might change after treatment there remains limited
information on the bacterial microbiome before and after surgical
removal of lesion (adenoma or carcinoma) and whether the community
changes at all.

In this study we tested the hypothesis that the bacterial microbiome
changes between pre (initial) and post (follow up) samples after removal
of a lesion (adenoma or carcinoma). Our analysis included both alpha and
beta diversity analysis along with investigation of individual
operational taxonomic units (OTUs). We also utilized Random Forest to
build models to classify either initial and follow up samples or lesion
and normal samples and then subsequently observe how these models, as
well as specific OTUs within them, performed pre and post surgery. We
also investigated the models for similar important OTUs to identify the
crucial OTUs for not only classifying initial and follow up samples but
also lesion or normal.

>>>>

Recently, there has been promising work on the bacterial microbiome and
it's ability to complement existing screening methods such as Fecal
Immunoglobulin Test (FIT) or act alone as a screening tool {[}3,4{]}.
There has also been research into how the bacterial microbiome could be
altered directly on tumor tissue itself {[}5{]}. A few studies have also
shown how this bacterial microbiome {[}6{]} or specific members within
it {[}7{]} could be directly involved with the pathogenesis of CRC.
These studies have helped to provide a tantalizing link between the
bacterial microbiome and CRC. Although these studies suggest that the
bacterial microbiome might change after treatment there remains limited
information on the bacterial microbiome before and after surgical
removal of lesion (adenoma or carcinoma) and whether the community
changes at all.

In this study we tested the hypothesis that the bacterial microbiome
changes between pre (initial) and post (follow up) samples removal of
lesion (adenoma or carcinoma). Our analysis included both alpha and beta
diversity analysis along with investigation of individual operational
taxonomic units (OTUs). We also utilized Random Forest to build models
to classify either lesion and normal samples or initial and follow up
samples and then subsequently observe how these models, as well as
specific OTUs within them, performed pre and post lesion removal. We
also investigated the models for similar important OTUs to identify the
crucial OTUs for not only classifying lesion or normalsamples but also
initial and follow up.
